DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-06-30 ase2017/paper.tex
reviewed experimental setup
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

For all evaluated benchmarks, the signal input range lies between $-1$ and $1$, and the implementation used for the integer part is $8$ bits, and for fractional part is also $8$ bits.
%
All experiments with \tool v$1$.$0$.$0$  were conducted on an otherwise idle Intel Core i$7-2600$ 
$3.40$ GHz processor, with $24$ GB of RAM, running Ubuntu $64$-bits.

>>>>

For all evaluated benchmarks, the signal input range related to the control system 
lies between $-1$ and $1$. The implementation features used for digital controller are:
$8$-bits for the integer part (including the sign bit) and $8$-bits for the fractional 
part. All experiments with \tool v$1$.$0$.$0$  were conducted on an otherwise idle 
Intel Core i$7-2600$ $3.40$ GHz processor, with $24$ GB of RAM, running Ubuntu $64$-bits.
